\morus: Biases in the Stream

### 2018-05-09 morusAC_01_Introduction.tex
bib, macros

Authenticated Encryption (AE) schemes combine the functionality of symmetric encryption schemes and message authentication codes.
Based on a shared secret key $K$, they encrypt a plaintext message $M$ to a ciphertext $C$ and authentication tag $T$ in order to protect both the confidentiality and the authenticity of $M$.
Most modern authenticated encryption algorithms are nonce-based schemes with associated data (AEAD),
where $(C, T)$ additionally depends on a unique nonce $N$ (or initialization value IV) and optional associated metadata $A$.
One of the most prominent standardized AEAD designs is \cipher{AES-GCM} \cite{TODOMV05,TODONIST},
which is widely deployed in protocols such as \cipher{TLS v1.3}.

@@

\todo[inline]{Related designs; Analysis of related designs; discuss \cite{sacryptMinaud14} on AEGIS \cite{AEGIS}}

>>>>

Authenticated Encryption (AE) schemes combine the functionality of symmetric encryption schemes and message authentication codes.
Based on a shared secret key $K$, they encrypt a plaintext message $M$ to a ciphertext $C$ and authentication tag $T$ in order to protect both the confidentiality and the authenticity of $M$.
Most modern authenticated encryption algorithms are nonce-based schemes with associated data (AEAD),
where $(C, T)$ additionally depends on a unique nonce $N$ (or initialization value IV) and optional associated metadata $A$.
One of the most prominent standardized AEAD designs is \cipher{AES-GCM} \cite{indocryptMcGrewV04,nistDworkin07},
which is widely deployed in protocols such as \cipher{TLS v1.3}.

@@

\todo[inline]{Related designs. Brice, do you want to add a sentence to discuss \cite{sacryptMinaud14} on AEGIS \cite{AEGIS}?}
